\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-12-16 ase20/intro.tex
IEEETran format for ASE'20

In this paper, we propose JavaScript IR-based Semantics Extraction
Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
syntax and semantics from the ECMAScript specification.  It
automatically generates a JavaScript parser from the syntax defined in
the ECMAScript specification.  It also automatically extracts the
formal semantics of JavaScript with given \textit{compile rules}.
Each compile rule describes how abstract algorithms in the
specification written in a natural language are converted into
functions of our intermediate representation \( \ires \).  In
addition, to save the labor of defining such compile rules, we also
present a \textit{rule generation assistant}, which suggests new
compile rules based on fault localization of not yet convertible
algorithms.  The assistant helps us deal with changed or newly
introduced algorithms defined in new versions of the ECMAScript
specification as well.

>>>>

In this paper, we propose JavaScript IR-based Semantics Extraction
Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
syntax and semantics from the ECMAScript specification.  It
automatically generates a JavaScript parser from the syntax defined in
the ECMAScript specification.  It also automatically extracts the
formal semantics of JavaScript with given \textit{compile rules}.
Each compile rule describes how abstract algorithms in the
specification written in a natural language are converted into
functions of our intermediate representation \( \ires \).  In
addition, to save the labor of defining such compile rules, we also
present a \textsf{Fault Localizer}, which suggests new
compile rules based on fault localization of not yet convertible
algorithms.  It helps us deal with changed or newly
introduced algorithms defined in new versions of the ECMAScript
specification as well.

### 2019-12-16 ase20/main.tex
IEEETran format for ASE'20

\documentclass[sigconf,review,anonymous=true]{acmart}

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

% removed ACM references
\settopmatter{printacmref=false}

@@

\author{Jihyeok Park}
\email{jhpark0223@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Jihee Park}
\email{j31d0@kaist.ac.kr}
\affiliation{\institution{KAIST}}

\author{Sukyoung Ryu}
\email{sryu.cs@kaist.ac.kr}
\affiliation{\institution{KAIST}}

@@

\keywords{
  JavaScript,
  mechanized formal semantics,
  program synthesis
}

>>>>

\documentclass[10pt,conference,anonymous=true]{IEEEtran}

\usepackage{url}
\usepackage{amsmath, amssymb}
\usepackage{natbib}
\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

@@

\author{\IEEEauthorblockN{Jihyeok Park}
  \IEEEauthorblockA{\textit{KAIST}}
  Daejeon, South Korea \\
  jhpark0223@kaist.ac.kr

  \and

  \IEEEauthorblockN{Jihee Park}
  \IEEEauthorblockA{\textit{KAIST}}
  Daejeon, South Korea \\
  j31d0@kaist.ac.kr

  \and

  \IEEEauthorblockN{Sukyoung Ryu}
  \IEEEauthorblockA{\textit{KAIST}}
  Daejeon, South Korea \\
  sryu.cs@kaist.ac.kr
}

@@

\begin{IEEEkeywords}
  JavaScript,
  mechanized formal semantics,
  program synthesis
\end{IEEEkeywords}

### 2019-12-16 ase20/overview.tex
IEEETran format for ASE'20

\textbf{Outline.}
In the remainder of this paper, we describe the detailed techniques of
\( \tool \).  We first formally define \( \bnfes \) and how to
automatically generate parsers from given \( \bnfes \) using lookahead
parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
abstract algorithms with tagged tokens into \( \ires \) functions using
compile rules, and introduce a rule generation assistant to
easily construct compile rules (Section~\ref{sec:compiler}).  After
describing implementation details (Section~\ref{sec:impl}),
we evaluate the effectiveness of \( \tool \)
(Section~\ref{sec:eval}), discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).

>>>>

\textbf{Outline.}
In the remainder of this paper, we describe the detailed techniques of
\( \tool \).  We first formally define \( \bnfes \) and how to
automatically generate parsers from given \( \bnfes \) using lookahead
parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
abstract algorithms with tagged tokens into \( \ires \) functions using
compile rules, and introduce a fault localization algorithm to
easily construct compile rules (Section~\ref{sec:compiler}).  After
describing implementation details (Section~\ref{sec:impl}),
we evaluate the effectiveness of \( \tool \)
(Section~\ref{sec:eval}), discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).
